---
title: "P8105 hw2 "
author: "Jiawei Ye"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
```

##Problem 1
The following code chunk reads the data and do some cleaning.
```{r read_clean}
data_read = read.csv("./data/NYC_Transit_Subway_Entrance_And_Exit_Data.csv") %>% 
  janitor::clean_names()
nyc_transit = select(data_read, line:vending, ada, -exit_only) %>% 
  mutate(entry = recode(entry,"YES" = TRUE, "NO" = FALSE))
names(nyc_transit)
```

The above code chunk retained variables about the station and discarded the variables about the entrances of the station. It also changed the value of `entry` variable into logical value. The dimension of the dataset is `r nrow(nyc_transit)` rows and `r ncol(nyc_transit)` columns.  

Each observation in the dataset is a subway station entrances/exits in NYC, the variables describe stations name of the entrance/exit, the routes that run through it, the latitude and logitude of the station and ways to enter each station, whether the entrance/exit has a vending allow entrance, and ADA compliance.  

The dataset is not really tidy enough. The `route` variable needs to be combined in some way.  
```{r info_nyc_transit}
nrow(distinct(nyc_transit, station_name, line))
sum(nyc_transit$ada)
vending_proportion = 100 * nrow(filter(nyc_transit, vending == "NO"))/nrow(nyc_transit)
```

The output shows that there are `r nrow(distinct(nyc_transit, station_name, line))` distinct stations. `r sum(nyc_transit$ada)` stations are ADA compliant. `r round(vending_proportion,2)`% of the entrance/exits is not vending allowed.  

```{r reformat_data}

```

##Problem 2
```{r loading}
mtw = read_excel("./data/HealthyHarborWaterWheelTotals2017-9-26.xlsx", 
                 sheet = 1, range = cell_cols("A:N")) %>% 
  janitor::clean_names() %>% 
  filter(dumpster != "NA")
mtw
```

